Coherent optical association of a single molecule

### 2020-10-08 paper.tex
Update number

Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
the linewidth of the $v'=0$ excited state is no larger than $50 \mathrm{MHz}$.
This suggests that the excited state linewidth should not cause a stronger than expected
scattering from $v'=0$ state either.

>>>>

Based on our previous measurements of the excited state using photoassociation (PA) spectroscopy,
the linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$.
This suggests that the excited state linewidth should not cause a stronger than expected
scattering from $v'=0$ state either.
